Clustering Beat-Chroma Patterns in a Large Music Database

### 2010-03-23 Paper/Paper.tex
better codes displayed
code display improved
new figure: freqs, added

The 25 most frequently used codewords in the test set are shown in
Figure \ref{fig:codes1}.  The codewords primarily consist of sustained
notes and simple chords.  Since they are designed to be key-invariant,
specific notes do not appear.  Instead the first 7 codewords
correspond to a single note sustained across two bars (codeword 1),
perfect fifth (codes 2 and 3) and fourth intervals (codes 4 7), and a
major and minor triads (code 6 and 5).  Many of the remaining
codewords correspond to common transitions from one chord to another,
\eg a transition from one major triad to another (\ie Cmaj
$\rightarrow$ Fmaj assuming that chroma 0 is C) in codes 8 and 10 and
the reverse transition in code (\ie Fmaj $\rightarrow$ Cmaj) in code
22.  Does this transition have a better name like ``relative x''?

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{codes1}
\end{center}
\caption{\small{
Most used codes in the codebook in term of frequency of use in the test
set (artist20, see Subsection \ref{ssec:artist}). 
This codebook was of size $200$ and trained on $2$ bars, pattern
size is $12$x$8$. Code in Figure \ref{fig:code} is the $8$th most used
here (second row, third column). Over the patterns, we display the number of
times it was used out of $71832$ total patterns in the dataset.
}}
\label{fig:codes1}
\end{figure}

>>>>

The 25 most frequently used codewords in the test set are shown in
Figure \ref{fig:codes1}.  
The frequency of use of these codewords are shown in Figure \ref{fig:freqs}.
The codewords primarily consist of sustained
notes and simple chords.  Since they are designed to be key-invariant,
specific notes do not appear.  Instead the first 7 codewords
correspond to a single note sustained across two bars (codeword 1),
perfect fifth (codes 2 and 3) and fourth intervals (codes 4 7), and a
major and minor triads (code 6 and 5).  Many of the remaining
codewords correspond to common transitions from one chord to another,
\eg a transition from one major triad to another (\ie Cmaj
$\rightarrow$ Fmaj assuming that chroma 0 is C) in codes 8 and 10 and
the reverse transition in code (\ie Fmaj $\rightarrow$ Cmaj) in code
22.  Does this transition have a better name like ``relative x''?

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{codes1}
\end{center}
\caption{\small{
Most used codes in the codebook in term of frequency of use in the test
set (artist20, see Subsection \ref{ssec:artist}). 
This codebook was of size $200$ and trained on $2$ bars, pattern
size is $12$x$8$. Code in Figure \ref{fig:code} is the $8$th most used
here (second row, third column). 
Numbers display are the index (from most used to least) and in parentheses
the percentage of use in the whole collection times $100$.
There is $71832$ patterns in total in the dataset.
}}
\label{fig:codes1}
\end{figure}

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.7\columnwidth]{freqs}
\end{center}
\caption{\small{
Frequency of use of the patterns in Figure \ref{fig:codes1} on the
artist20 dataset.
There is $71832$ patterns in total in the dataset.
}}
\label{fig:freqs}
\end{figure}
